Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2023-01-11 edubots_surveys.Rnw
Update edubots_surveys.Rnw
Co-authored-by: Francisco Barranco <fbarranco@ugr.es>

Furthermore, the answers to the survey question regarding COVID-19 highlights the
significant challenge of altering behavior, even during a major crisis. Very few
responders actually changed their habits, although comparing women vs. men as
well as those teaching social sciences vs. the rest of the disciplines, there
are some significant differences. We do not have a clear understanding of the
reasons behind this behavior; however, it appears that the perception and
adoption of technologies in a major crisis may vary based on an individual's
background and gender.

One of the most interesting questions arising from the analysis of the results,
and that should require further study, is: Are teachers really aware of the
possibilities of chatbots in the classroom? The survey only listed a few
functionalities for the chatbots, and just a few subjects selected the option
``Others''. This may suggest that most teachers did not really understand at
this point the actual potential of chatbots, since the responses listed were by
no means exhaustive. Had the responders been more acquainted with the
possibilities of this technology, this ``Other'' response would possibly have
shown up many more times. Another way to look at it is that, unless you provide
the specific instructions on how to use a tool, the teaching staff is already
too busy or burnt out to think about innovation, so they think it is not their
job to think about new possibilities of existing or new technologies.

>>>>

Furthermore, the answers to the survey question regarding COVID-19 highlights the
significant challenge of altering behavior, even during a major crisis. Very few
responders actually changed their habits, although comparing women vs. men as
well as those teaching social sciences vs. the rest of the disciplines, there
were some significant differences. We do not have a clear understanding of the
reasons behind this behavior; however, it appears that the perception and
adoption of technologies in a major crisis may vary based on an individual's
background and gender.

One of the most interesting questions arising from the analysis of the results,
and that should require further study, is: Are teachers really aware of the
possibilities of chatbots in the classroom? The survey only listed a few
functionalities for the chatbots, and just a few subjects selected the option
``Others''. This may suggest that most teachers did not really understand at
this point the actual potential of chatbots, since the responses listed were by
no means exhaustive. Had the responders been more acquainted with the
possibilities of this technology, this ``Other'' response would possibly have
shown up many more times. Another way to look at it is that, unless you provide
the specific instructions on how to use a tool, the teaching staff is already
too busy or burnt out to think about innovation, so they likely consider that it is not their
job to think about new possibilities of existing or new technologies.
